Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-03 code/rmarkdown/article.Rmd
+ included missing ref

### Adaptive and neutral genetic data
To investigate the effectiveness of the surrogates for adaptive and neutral genetic variation, we first needed to identify which of the sampled loci--if any--were under selection. We used two outlier detection methods to achieve this. We omitted the species \textit{`r missing.species`} from all subsequent analyses because it was not compatible with one of the outlier detection methods (see below). The basic premise underpinning such methods is that neutral loci are expected to exhibit a specific level of variation among populations, and loci that deviate from this expectation should be under selection [reviewed in @r480]. The advantage of these methods--in contrast with environmental association analyses [@r489]--is that they do not use environmental data to identify loci under selection, which would have biased our analysis. Loci identified as outliers in both analyses were treated as adaptive and the rest were treated as neutral. To avoid false-positives, we omitted loci from both outlier detection methods where the global frequency of the minor allele was $\geq 0.1$ and assumed they were neutral.

@@

We then fit maximum likelihood population-effects (MLPE) models [implemented in the \texttt{ResistanceGA R} package; @r488]. These models explicitly accommodate the structure of dissimilarity matrices using random effects [@rXXX]. For each species, we fit a MLPE model to correlate the species' dissimilarity matrices based on geographic position and neutral genetic variation. Additionally, if the species was associated with adaptive loci, we also fit a MLPE model to correlate the species' dissimilarity matrices calculated using enviuronmental conditions and adaptive genetic variation. To test if the surrogate variables explained a substantial amount of genetic variation, we conducted $\chi^2$ tests between each model and its corresponding null model, and Bonferroni corrections.

>>>>

### Adaptive and neutral genetic data
To investigate the effectiveness of the surrogates for adaptive and neutral genetic variation, we first needed to identify which of the sampled loci--if any--were under selection. We used two outlier detection methods to achieve this. We omitted the species \textit{`r gsub('_', ' ' , missing.species, fixed=TRUE)`} from all subsequent analyses because it was not compatible with one of the outlier detection methods (see below). The basic premise underpinning such methods is that neutral loci are expected to exhibit a specific level of variation among populations, and loci that deviate from this expectation should be under selection [reviewed in @r480]. The advantage of these methods--in contrast with environmental association analyses [@r489]--is that they do not use environmental data to identify loci under selection, which would have biased our analysis. Loci identified as outliers in both analyses were treated as adaptive and the rest were treated as neutral. To avoid false-positives, we omitted loci from both outlier detection methods where the global frequency of the minor allele was $\geq 0.1$ and assumed they were neutral.

@@

We then fit maximum likelihood population-effects (MLPE) models [implemented in the \texttt{ResistanceGA R} package; @r488]. These models explicitly accommodate the structure of dissimilarity matrices using random effects [@r494]. For each species, we fit a MLPE model to correlate the species' dissimilarity matrices based on geographic position and neutral genetic variation. Additionally, if the species was associated with adaptive loci, we also fit a MLPE model to correlate the species' dissimilarity matrices calculated using enviuronmental conditions and adaptive genetic variation. To test if the surrogate variables explained a substantial amount of genetic variation, we conducted $\chi^2$ tests between each model and its corresponding null model, and Bonferroni corrections.
